---
title: "Drive Thru COVID-19 Testing Data Results"
format:
  html:
    theme: journal

execute:
  echo: false #hide code
  error: true #run even if errors occur
---

```{r}
#| message: false

# Load data
library(tidyverse)
library(gtsummary)
library(here)
library(janitor)
library(Hmisc)
library(summarytools)
library(ggplot2)
library(broom.helpers)
library(cardx)

#Import Data
raw_data <- readRDS(here::here("data/raw/raw_data.rds"))
#Drop unnecessary variables and NA
edited <- raw_data |>
										select(c(subject_id, age, clinic_name,
																			gender, test_id, result, drive_thru_ind,
																			col_rec_tat, rec_ver_tat)) |>
   na.omit() |>
	
#Label data
		mutate(drive_thru_ind = factor(drive_thru_ind,
																	 levels = c(0,1),
																	 labels = c("No", "Yes")))

label(edited$col_rec_tat) <- "Time (hours) between collection and lab received"
label(edited$rec_ver_tat) <- "Time (hours) between received and test verification"


```
## Table 1 - Summary Statistics


```{r}
#Load table
#| echo: false


table1 <- tbl_summary(
	edited,
	by = gender,
	include = c(age, result, drive_thru_ind, col_rec_tat,
							rec_ver_tat)) |>
	add_overall(last = TRUE)
table1

pos_test <- inline_text(table1, variable = "result", level = "positive", column = "stat_0")

```
The median and IQR for age is `r gtsummary::inline_text(table1, variable = "age")` years old.

The overall positive test results are `r pos_test` out of the total **15,524** tests conducted.



## Regression Results 
Dependent variable is y= age, regressed off of the following variables: result, gender, and clinic name

```{r}
#Create regression
tbl_uvregression(
	edited,
	y = age,
	include = c(result, gender, clinic_name),
	method = lm)

```

## Figure 1 - Boxplot of test results and age
Results are color coded with the key in the graph

```{r}
#Create figure1

figure1 <- ggplot(data=edited, aes(x=result, y=age, fill= result)) +
		geom_boxplot() +
	scale_fill_manual(values=c("grey", "red", "green")) + #adds manual colors in order of result
	theme_minimal() #adds white background
figure1
```

The `echo: false` option disables the printing of code (only output is displayed).
